What We Eval in the Shadows

### 2021-08-06 paper/main.tex
Provenance
Move Unnecessary Uses of Eval section

\begin{compactitem}[---]
\item {\it Constructed:} Expressions can be constructed by invoking the
  \c{quote}, \c{enquote}, \c{expression} functions, or by building a call with \c{call} or \c{as.call}.
\item {\it Reflection:} This group corresponds to uses of \c{match.call} to
  reflectively capture the expression that invoked the current function. Function arguments are passed as promises, and \c{substitute} is used to retrieve the source
  expression associated with the promise. \c{formals} access the argument list of a function.
\item {\it String:} Expressions created from strings by invoking \c{parse},
  \c{str2expression}, or \c{str2lang}.
\item {\it Environment: }   a symbol is created with \c{as.name} or \c{as.symbol}, typically to find the value of a symbol in a non-local environment.
\end{compactitem}

@@

\subsection{Unnecessary use of \eval}

@@

\subsection{Alternatives to \eval}

Talk about lazyeval and tidyeval

>>>>

\begin{compactitem}[---]
\item {\it Constructed:} Expressions can be constructed by invoking the
  \c{quote}, \c{enquote}, \c{expression} functions, or by building a call with \c{call} or \c{as.call}.
\item {\it Reflection:} This group corresponds to uses of \c{match.call} to
  reflectively capture the expression that invoked the current function. Function arguments are passed as promises, and \c{substitute} is used to retrieve the source
  expression associated with the promise. \c{formals} access the argument list of a function.
\item {\it String:} Expressions created from strings by invoking \c{parse},
  \c{str2expression}, or \c{str2lang}.
\item {\it Environment: }   A symbol is created with \c{as.name} or \c{as.symbol}, typically to find the value of a symbol in a non-local environment.
\end{compactitem}

@@

\subsection{Alternatives to \eval}
Talk about lazyeval and tidyeval

\subsection{Removing \eval}

@@
